Proportional multi-state multiple-cohort life table model

### 2018-04-16 MSLT/MSLTdoc.Rmd
Issues with loop for GBD_plot

ALSO PART OF THE BELOW CODE WILL BE NEEDED FOR THE MSLT AND DISMOD COLLECTION. GENERATE DATA INPUTS FOR DISMOD II FROM HERE. These data should be used to generate the general life table and disease life tables (Figure 3).

@@

p_sex <- c("male", "female")
p_cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancers", "breast cancer", "tracheal, bronchus, and lung cancer")
p_measure <- c("all causes", "ylds (years lived with disability)", "prevalence", "incidence")

>>>>

These data should be used to generate the general life table and disease life tables (Figure 3).

@@

p_sex <- c("male", "female")
p_cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancers", "breast cancer", "tracheal, bronchus, and lung cancer")
p_measure <- c("deaths", "ylds (years lived with disability)", "prevalence", "incidence")
